Addendum to Manhattan Scene Understanding Using Monocular, Stereo, and 3D Features

### 2012-06-01 papers/eccv2010/rebuttal/rebuttal-v1.txt

We thank all three reviewers for their positive comments as well as constructive criticism.

A key concern raised by all three reviewers is the apparently restrictive nature of the proposed indoor Manhattan models. Since this constitutes by far the most frequent objection, and indeed is the only substantial complaint of Reviewer 5, we dedicate the following four paragraphs to responding to this issue.

It must be stressed that our aim is to recover _coarse_, _high-level_ models in order to obtain useful geometric cues that will assist further reasoning, rather than to recover intricately detailed 3D models of the environment. Given the ill-posed nature of the single-view reconstruction problem, it seems obvious to us that there is a trade-off between the complexity of models on one hand and the robustness of the estimation process on the other. We believe that indoor Manhattan model represent an ideal point on this trade-off curve since they capture an excellent set of geometric properties (such as the dominant surface orientations, height of the floor and ceiling w.r.t the camera, and the position of major room boundaries) while retaining a low-dimensional parameterization.

In addition to the robustness argument above, there is a further advantage to our use of indoor Manhattan models: the position of room boundaries, which our models recover explicitly, will prove more salient for purposes such as navigation, scene classification, or contextual priming of object detection, than the detailed geometry of room clutter. On this view the choice of indoor Manhattan models constitutes an effort to recover room boundaries _in spite_ of scene clutter,  and indeed our system is able to achieve precisely this (see rows 1-7 of Figure 2 in supplementary material).

We further note that previous attempts at single-view reconstruction have (necesarily) encountered the same robustness/complexity trade-off, and most have indeed chosen to restrict the class of scene models. Lee [4] and Flint [5] employ exactly the same class of models as us, while Hedau et al. [12] choose the far more restricted class of simple cuboids. Hoiem et al. [10] also restricts surface orientations to three dominant directions; only Saxena et al. [11] allow more general models, though they do not evaluate their system on difficult indoor scenes.

It seems appropriate to briefly sketch some concrete examples of "high-level reasoning systems" that would benefit from being able to recover indoor Manhattan models. A few examples are:
- Contextual cues for object detection, in the style pioneered by Torralba ("Contextual priming for object detection", IJCV 2003) and demonstrated for outdoor scenes by Hoiem ("Putting objects in perspective", IJCV, 2008). It seems obvious that "distance from the ground", "heigh relative to floor-ceiling distance", and "distance from nearest wall" would make extremely powerful cues when detecting objects in indoor scenes.
- Categorizing scenes into semantic categories such as "kitchen" or "bedroom", such as that investigated by Fei-Fei et al. ("A bayesian hierarchical model for learning natural scene categories", CVPR 2005). Incorporating cues such as the dimensions and shape of a room, as well as taking surface boundaries and orientation into account when reasoning from photometric cues, would constitute a powerful addition to texture-only approaches taken previously.
- High-level descriptions of room boundaries would find many uses for the purpose of path-planning and navigation in mobile robotics.

Reviewer 2 requests that we include the optimal substructure proof in the main text. We agree and have re-worked the layout of the final paper in order to achieve this.

We also thank reviewer 2 for pointing out the work of Barinova et al. Their work does not overlap with our approach (they use CRFs together with an EM algorithm) nor is a comparison with their results appropriate (their approach is suited only to outdoor scenes); we do, however, regret that this citation was omitted from the review manuscript and have added it to the final version. We also thank reviewer 3 for the reference to the work of Felzenszwalb and Vexler, but since this work is to appear at CVPR later this year we obviously could not have cited it in the review manuscript since it was not available at that time. Furthermore, our approach is quite different to theirs.

In response to the question raised by reviewer 2 regarding the ligitimacy of our evaluation framework, we respond that we chose the pixelwise evaluation metric in line with that chosen by Hoiem [10], Lee [4], and Hedau [12], and in order to allow direct comparisons with those approaches.

Reviewer 5 construes our approach as a "smoother" of the provided orientation estimate. Perhaps the reviewer has misunderstood the relationship of our work to that of Lee et al: We employ their plane sweep heuristic to obtain noisy orientation estimates as depicted in the second column of figures 3, 4, 5, and 6 (supplementary material). Importantly, our system does _not_ use the output of the branch-and-bound algorithm they employ; rather, our dynamic programming solution represents an alternative to their algorithm and we _compare_ our results to theirs.

Finally, to answer reviewer 5's question about our ground truth acquisition: it was obtained by hand-labelling structure-from-motion maps as described in the first paragraph of section 7. Small inaccuracies may arise from human error or structure-from-motion errors, but we see no evidence for systematic bias here.

### 2012-06-01 papers/eccv2010/rebuttal/rebuttal.txt

We thank the reviewers for positive comments and constructive criticism.

A key concern raised by the reviewers is the apparently restrictive nature of the indoor Manhattan model. We therefore stress that our proposed method recovers the dominant 3D structure of the environment while remaining robust to clutter. The gain in complexity compared to the state-of-the-art (Lee et al. [4]) is substantial, dropping from exponential to linear. Our approach also provides high-level geometric features, which are not simply pixel-wise orientations but meaningful large planar regions in the environment, encoding strong constraints for many tasks such as scene classification and contextual priming of object detection.

Our choice of the indoor Manhattan model constitutes an effort to recover room boundaries _in spite_ of scene clutter, and indeed our system is able to achieve precisely this (see rows 1-7 of Fig 2 in supp. material). We hope these figures explicitly answer the criticisms of R2 and R5 regarding robustness to clutter.

Previous attempts at single-view reconstruction have (necessarily) encountered the same robustness/complexity trade-off, and most have indeed chosen to restrict the class of scene models. [4] and [5] employ exactly the same class of models as us, while [12] choose the far more restricted class of simple cuboids. [10] also restrict surface orientations to three dominant directions; only [11] allow more general models, though they do not evaluate their system on indoor scenes.

We regret overlooking the work of Barinova et al pointed out by R2, and will rectify this in the final version. We thank R3
for highlighting the latest work by Felzenszwalb and Veksler that will appear at CVPR2010.

R2 and R5 question our evaluation framework. While there are indeed issues with the pixel-wise accuracy metric, it was previously used by Hoiem et al. [10], Lee et al. [4], and Hedau et al. [12], and so we adopted it to allow direct comparisons with those approaches. To answer the question raised by R5 regarding the method of ground truth acquisition: we used hand-labelled structure-from-motion maps as ground truth (lines 293-296). There may be small human- or structure-from-motion errors, but we do not believe there is systematic bias. R3 noted that our framework "very convincingly shows superiority over Lee et al" and was impressed by our automated ground truth acquisition mechanism.

R2 noted that the optimal substructure proof was interesting and should be included in the main paper. We will include the proof as recommended.

R5 construes our approach as a "smoother" of the initial orientation estimate. To clarify the relationship of our work to Lee et al: we employ their plane sweep heuristic to obtain noisy orientation estimates as depicted in the second column of Figs 3,4,5,6 (supp. material), but our system does _not_ use the output of the branch-and-bound algorithm they employ; instead, our dynamic programming solution represents a much more efficient alternative to their algorithm and we _compare_ our results to theirs.

### 2014-07-24 iccv2011/rebuttal.txt

We thank all reviewers for encouraging and constructive reviews. We are pleased that all reviewers offered broad encouragement of our approach and noted general satisfaction with our results. We are confident that we can address all suggestions and clarification requests in the camera-ready manuscript.

R1 requested several clarifications, each of which we have addressed in the final paper; we summarise the answers below:
1) Regarding occlusions- we assume locally convex environments (lines 408-417); this is violated surprisingly rarely since we are always interested in the boundaries of the environment and never the objects or clutter within. This means the DP optimization simply ignores occlusions. When we do encounter non-convex environments we find that global optimization together with a prior on model complexity (eq. 4) produces pleasing results regardless.
2) Features- we perform intensity and contrast normalization but we do not handle specularities or other non-linear lighting phenomena. Our intention is to show that models from stereo vision fit naturally into our framework; fully leveraging the best modern stereo algorithms remains future work.
3) Training- We trained and evaluated on separate sets of sequences. No place or room observed in the training set was also present in the test set.
4) Inference- All our experiments were performed with 2 auxiliary frames, which were sampled 1 second before and after each base frame. In the video sequence we selected base frames at 8-second intervals, and at each step we discarded the previous model and re-estimated. Each video frame shows the most recent model re-projected into the current frame.
5) Timing- We include further timing results in the final paper in line with the request by R2. Training on 150 frames takes roughly 15 minutes.

We thank R2 for two suggested citations. The work in (Lee et al, 2010) is relevant to ours primarily via earlier work (Lee et al, CVPR 2009), which our paper cited. We have added a citation for (Hedau et al, 2009), though our paper overlaps only marginally with this monocular approach. We regret that R2 found Section 3 unclear and we will revise extensively for the final submission. We have added timing results to the final paper as requested; we regret that this was omitted from the review manuscript.

We agree with R3 regarding overlap with [7]. We intended this paper to be understandable on its own since [7] was published less than a year ago and is not widely known, so we compromised by repeating some of their results during lines 530-553. We were aware of Erick Delage's early work in this area and regret omitting that citation; we have rectified this in our final submission. Regarding comparison with [7], the "Monocular only" line in Figure 8 is identical to the system of [7]; our final paper states this explicitly. (Compared to [7], the addition of stereo and 3D features reduces mean depth error by 10%.)

### 2014-07-24 iccv2011/final_addendum.tex
move papers/* to top level

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{array}

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pdftitle={Flint2011.pdf},pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

@@

%%%%%%%%% TITLE
\title{Manhattan Scene Understanding Using Monocular, Stereo, and 3D Features}

@@

%%%%%%%%% BODY TEXT
\input{main}

>>>>

\documentclass[10pt,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{array}
\usepackage{xtab}

@@

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

@@

%%%%%%%%% TITLE
\title{Addendum to Manhattan Scene Understanding Using Monocular, Stereo, and 3D Features}

@@

%%%%%%%%% BODY TEXT
\input{main_addendum}
